Efficient modeling of timeouts in PRISM \\

### 2018-06-27 Report/tool_paper.tex
change in the tool paper

\lstset{frame=tb,
	language=Java,
	aboveskip=1mm,
	belowskip=1mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\fontsize{8.8}{8.5}\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3,
	morekeywords={event, gsmp, dirac, exponential, uniform, weibull, erlang,
		module, init, rewards, endrewards, label, true, endmodule}
}

@@

	\begin{figure}[H]
		\centering
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm,
		semithick]
		\tikzstyle{every state}=[fill=white,draw=black,text=black]

		\node[initial,state] (s0)                    {$0$};
		\node[state]         (s1) [right of=s0] {$1$};
		\node[state]         (s2) [right of=s1] {$2$};
		\node[state]         (s3) [right of=s2] {$3$};
		\node[state]         (s4) [right of=s3]       {$4$};
		\node[state]         (sw) [right of=s4,fill=white,text=black]       {...};
		\node[state]         (sn) [right of=sw]       {$10$};

>>>>

\lstset{frame=tb,
	language=Java,
	aboveskip=1mm,
	belowskip=1mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\fontsize{8.8}{8.5}\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3,
	morekeywords={ctmc,event, gsmp, dirac, exponential, uniform, weibull, erlang,
		module, init, rewards, endrewards, label, true, endmodule}
}

@@

	\begin{figure}[H]
		\centering
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.67cm,
		semithick]
		\tikzstyle{every state}=[fill=white,draw=black,text=black]

		\node[initial, initial text ={},state] (s0)                    {$0$};
		\node[state]         (s1) [right of=s0] {$1$};
		\node[state]         (s2) [right of=s1] {$2$};
		\node[state]         (s3) [right of=s2] {$3$};
		\node[state]         (s4) [right of=s3]       {$4$};
		\node[state]         (sw) [right of=s4,fill=white,text=black]       {...};
		\node[state]         (sn) [right of=sw]       {$10$};
